Run Life expectancy and decomposition calculations

### 2017-01-20 Code/1_Explore_Data.Rmd
cleaning up

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.Rdata", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.Rdata", col_names = T)

>>>>

```{r write_data_to_csvs}
#save.image(file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/Sep6_BWgap.Rdata")
write_csv(dat.clean, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", col_names = T)
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", col_names = T)

### 2017-01-20 Code/2_Run_LE_and_Decomp_Calcs.Rmd
cleaning up

```{r load_data}
dat.aggregated <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.Rdata", header = T)
dat.clean<- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.Rdata", header = T)
```

@@

dat.clean$StateYearSex <- interaction(dat.clean$State_factor, dat.clean$Year_factor, dat.clean$Sex_factor)

@@

@@

       list.cod.decomp.tables[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")

>>>>

```{r load_data}
dat.aggregated <- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated.csv", header = T)
dat.clean<- read.csv("/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_clean.csv", header = T)
```

@@

@@

```{r save_objects}
write_csv(dat.aggregated, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/dat_aggregated2.csv", col_names = T)
write_csv(BlackWhite, path = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/BlackWhite.csv", col_names = T)

save(paired.ids, non.zero.stratums,
     list.age.decomp.tables1, list.age.decomp.tables5, list.age.decomp.tables9,
     list.life.tables1, list.life.tables5, list.life.tables9,  
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/calculated_data.Rdata")
```

#stopped here!

@@

       list.cod.decomp.tables[[i]] <- make_dataset_cod_plot(cod.decomp.table = list.cod.decomp.tables1[[i]],
                                                            age.groups = "Ages", 
                                                            cause.of.death = "Cause.of.death", 
                                                            sign.var = "sign", decomp.var = "C_xi", 
                                                            decomp.var.prop = "C_xi_proportion")
